The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
reflow
mv metric interpretations into comment

## Each metric's interpretation
**[JWT: Do we need to define degree first since degree is mentioned in so many of our definitions?]**
* Degree: the number of direct connections an individual has to other individuals in the network. High degree = connected to many indviduals in a single layer. Low degree = not connected to many individuals in a single layer.

@@

>>>>

<!--
## Each metric's interpretation

**[JWT: Do we need to define degree first since degree is mentioned in so many of our definitions?]**
* Degree: the number of direct connections an individual has to other individuals in the network. High degree = connected to many indviduals in a single layer. Low degree = not connected to many individuals in a single layer.

@@

-->
